\bf An observational study of papers published in \emph{PLOS ONE} and studies posted to a trial registry.

### 2021-04-20 manuscript/asa_template/asa_template.Rmd
tidy up folder structure

There is guidance for researchers on how to write up their statistical methods and results.
The International Committee of Medical Journal Editors recommend that researchers should: “Describe statistical methods with enough detail to enable a knowledgeable reader with access to the original data to judge its appropriateness for the study and to verify the reported results” [@ICMJE2019]. 
More detailed guideance is given by the SAMPL and EQUATOR guidelines [@Lang2013;@Altman2016] with the latter covering all apsects of the paper. Both of these guidelines were led by Doug Altman, who spoke often and for many years about the need for better statistical reporting. 
The awareness and use of these guidelines could be improved. There were 256 Google Scholar citations to the SAMPL paper (as at 15 March 2021) which is a good citation statistic for most papers, but is low considering the millions of papers that use statistical analysis.
<!--- Although the general lack of statistical understanding from both authors and reviewers means this recommendation may not be checked. --->

@@

The ANZCTR was established in 2005 as part of a coordinated global effort to improve research quality and transparency in clinical trials reporting; observational studies can also be registered. All studies registered on ANZCTR are publicly available and can be searched via an online portal (https://www.anzctr.org.au). 
<!--- Researchers responsible for overseeing a clinical trial are expected to register full details before commencing participant enrolment. --->
Details required for registration follow a standardised template [@ANZCTR], which covers participant eligibility, the intervention(s) being evaluated, study design and outcomes. The information provided must be in English. Studies are not peer reviewed.

@@

![\label{fig:plos-n}A: Search results by _PLOS ONE_ volume; B: word count per statistical methods section included in analysis (n = 111,73); C: subject classifications assigned to full-text records included in analysis](figures/figure1.jpg)

@@

![\label{fig:plot-10-topics}Topic clouds summarising common terms in _PLOS ONE_ statistical methods sections assuming ten clusters](figures/figure2.jpg)

@@

The topic clouds based on ten clusters are in Figure~\@ref(fig:plot-10-topics). Frequently occurring words reflected the use of statistical software (Topics~3 and 5), descriptive statistics (Topic~6), group based hypothesis testing (Topics 1 and 4) and definitions of statistical significance (Topics~1 and 9). There are also statistical methods sections associated with regression (Topic~2) and meta-analysis (Topic~7).

>>>>

There is guidance for researchers on how to write up their statistical methods and results.
The International Committee of Medical Journal Editors recommend that researchers should: “Describe statistical methods with enough detail to enable a knowledgeable reader with access to the original data to judge its appropriateness for the study and to verify the reported results” [@ICMJE2019]. 
More detailed guideance is given by the SAMPL and EQUATOR guidelines [@Lang2013;@Altman2016] with the latter covering all apsects of the paper. Both of these guidelines were led by Doug Altman, who spoke often and for many years about the need for better statistical reporting. 
The awareness and use of these guidelines could be improved. There were 256 Google Scholar citations to the SAMPL paper (as at 15 March 2021) which is a good citation statistic for most papers, but is low considering the millions of papers that use statistical analysis.

@@

The ANZCTR was established in 2005 as part of a coordinated global effort to improve research quality and transparency in clinical trials reporting; observational studies can also be registered. All studies registered on ANZCTR are publicly available and can be searched via an online portal (https://www.anzctr.org.au).

Details required for registration follow a standardised template [@ANZCTR], which covers participant eligibility, the intervention(s) being evaluated, study design and outcomes. The information provided must be in English. Studies are not peer reviewed.

@@

![\label{fig:plos-n}A: Search results by _PLOS ONE_ volume; B: word count per statistical methods section included in analysis (n = 111,73); C: subject classifications assigned to full-text records included in analysis](figures/plos.summary.jpg)

@@

![\label{fig:plot-10-topics}Topic clouds summarising common terms in _PLOS ONE_ statistical methods sections assuming ten clusters](figures/plos.wordclouds.jpg)

@@

The topic clouds based on ten clusters are in Figure~\ref{fig:plot-10-topics}. Frequently occurring words reflected the use of statistical software (Topics~3 and 5), descriptive statistics (Topic~6), group based hypothesis testing (Topics 1 and 4) and definitions of statistical significance (Topics~1 and 9). There are also statistical methods sections associated with regression (Topic~2) and meta-analysis (Topic~7).

### 2021-04-20 manuscript/asa_template/asa_template.tex
update tex file
tidy up folder structure

The ANZCTR was established in 2005 as part of a coordinated global
effort to improve research quality and transparency in clinical trials
reporting; observational studies can also be registered. All studies
registered on ANZCTR are publicly available and can be searched via an
online portal (\url{https://www.anzctr.org.au}). Details required for
registration follow a standardised template \citep{ANZCTR}, which covers
participant eligibility, the intervention(s) being evaluated, study
design and outcomes. The information provided must be in English.
Studies are not peer reviewed.

@@

\begin{figure}
\centering
\includegraphics{figures/plosone.10topics.jpg}
\caption{\label{fig:plot-10-topics}Topic clouds summarising common terms
in \emph{PLOS ONE} statistical methods sections assuming ten clusters}
\end{figure}

@@

The topic clouds based on ten clusters are in
Figure\textasciitilde@ref(fig:plot-10-topics). Frequently occurring
words reflected the use of statistical software (Topics\textasciitilde3
and 5), descriptive statistics (Topic\textasciitilde6), group based
hypothesis testing (Topics 1 and 4) and definitions of statistical
significance (Topics\textasciitilde1 and 9). There are also statistical
methods sections associated with regression (Topic\textasciitilde2) and
meta-analysis (Topic\textasciitilde7).

>>>>

The ANZCTR was established in 2005 as part of a coordinated global
effort to improve research quality and transparency in clinical trials
reporting; observational studies can also be registered. All studies
registered on ANZCTR are publicly available and can be searched via an
online portal (\url{https://www.anzctr.org.au}).

Details required for registration follow a standardised template
\citep{ANZCTR}, which covers participant eligibility, the
intervention(s) being evaluated, study design and outcomes. The
information provided must be in English. Studies are not peer reviewed.

@@

\begin{figure}
\centering
\includegraphics{figures/figure2.jpg}
\caption{\label{fig:plot-10-topics}Topic clouds summarising common terms
in \emph{PLOS ONE} statistical methods sections assuming ten clusters}
\end{figure}

@@

The topic clouds based on ten clusters are in
Figure\textasciitilde{}\ref{fig:plot-10-topics}. Frequently occurring
words reflected the use of statistical software (Topics\textasciitilde3
and 5), descriptive statistics (Topic\textasciitilde6), group based
hypothesis testing (Topics 1 and 4) and definitions of statistical
significance (Topics\textasciitilde1 and 9). There are also statistical
methods sections associated with regression (Topic\textasciitilde2) and
meta-analysis (Topic\textasciitilde7).
